%!TEX root = ../thesis.tex

Over the last 3.5 years, I have received help and support from many individuals. First and 
foremost is my supervisor, Chris Hays, whom I was fortunate to work closely with. I thank him 
for his patience, and for our enlightening conversations on perturbative QCD, the brewing of 
fine beers and how to explain the hierarchy problem with plush toys.

The ATLAS \HWW analysis group is comprised of many students, post-docs and research fellows, 
all collaborating to achieve a common goal. I thank Jianming Qian, Biagio Di Micco, Pierre 
Savard, Tatsuya Masubuchi, Christian Schmitt and Corrinne Mills for successfully convening 
such a complex analysis. There are too many members of the analysis team for me to mention 
here, but I would particularly like to thank Jonathan Long, Keisuke Yoshihara, Olivier 
Arnaez and Magda Chelstowska. For their help and guidance in my work on theoretical 
uncertainties, I thank Chris Hays, Biagio Di Micco, Justin Griffiths, Bob Kehoe and Sara 
Diglio. I also thank the Higgs Cross Section Working Group for their feedback on the ggF jet 
binning studies, in particular Andrea Banfi, Gavin Salam and Frank Tackmann. I thank MCnet 
for their series of summer schools, the \sherpa authors for releasing a version that enabled 
the \Wgstar sample to be produced, and Stefano Frixione for his advice during my time at CERN.

For the \unit{7}{\TeV} \WW cross section measurement, I would like to thank Marc-Andre Pleier 
and Matthias Schott in their role as analysis convenors. I also thank Shu Li and Yusheng Wu, 
when we were endlessly poring over cutflows.

Within the Oxford ATLAS group, Todd Huffman and Tony Weidberg provided excellent supervision 
during my ATLAS service work project, and an introduction to Belgian nuclear reactors and 
beer (and why they should not be mixed). Thanks must also go to Gemma Wooden for getting me 
started in the \WW and \HWW analyses at a time when she was busy finishing her DPhil. I am 
truly grateful to Alex Dafinca and Lucy Kogan for sharing this experience from the start, and 
Jacob Howard for his overwhelming computing knowledge. I also thank Chris Y, Craig, Ellie, 
Jim, Kate, Mireia, Rob, Sarah and Shaun for office banter. Finally, I thank Sue Geddes and 
Kim Proudfoot for their help with administrative matters, and Oxford IT support for 
maintaining an excellent computer farm (on which I munched through 100,000 CPU hours).

I feel very lucky to have been a member of St Catherine's College during my DPhil. I've met 
such a variety of interesting characters in the Catz MCR, particularly in my 1st and 3rd 
years; it really has been a defining aspect of my time at Oxford University. Thanks for such 
great memories and I look forward to many more to come.

Of course, I also thank my parents, the rest of my family and my close friends for helping me 
through the difficult times.

Lastly, I thank the STFC for financially supporting me for the majority of the degree, and 
ACEOLE for granting me a bursary to speak at the TWEPP-11 conference in Vienna. I am also 
indebted to St Catherine's College for awarding me the College Science Scholarship in my 3rd 
year and a Light Senior Scholarship in my 4th year. They also provided other funding at 
various points throughout the degree, \eg enabling me to attend the CLASHEP-13 school in Peru.
